X-ray phase-contrast imaging at 100 keV on a conventional source

### 2013-11-29 hedpc.tex
new cover letter, added medical imaging keyword, fixed thomas name

\author{T.~Thüring%
\affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}%
\affil{2}{Institute for Biomedical Engineering,
    Swiss Federal Institute of Technology,
    Gloriastrasse 35,
8092 Zurich, Switzerland},%
M.~Abis%%
\affil{1}{}%
\affil{2}{},%
Z.~Wang%
\affil{1}{},%
C.~David%
\affil{1}{},%
\and%
M.~Stampanoni%
\affil{1}{}%
\affil{2}{}}

@@

%% When adding keywords, separate each term with a straight line: |
\keywords{X-ray phase contrast | grating interferometry | X-ray interferometry}

>>>>

\author{T.~Thuering%
\affil{1}{Paul Scherrer Institute, 5232 Villigen, Switzerland}%
\affil{2}{Institute for Biomedical Engineering,
    Swiss Federal Institute of Technology,
    Gloriastrasse 35,
8092 Zurich, Switzerland},
M.~Abis%%
\affil{1}{}%
\affil{2}{},
Z.~Wang%
\affil{1}{},
C.~David%
\affil{1}{},
\and%
M.~Stampanoni%
\affil{1}{}%
\affil{2}{}}

@@

%% When adding keywords, separate each term with a straight line: |
\keywords{X-ray phase contrast | grating interferometry | X-ray
interferometry | medical imaging}
